Evidence accumulation modelling offers new insights into the cognitive mechanisms that underlie linguistic and action-based training

### 2025-04-01 manuscript/manuscript.Rmd
minor updates to the manuscript

---
title             : "Evidence accumulation modelling offers new insights into the cognitive mechanisms that underlie linguistic and action-based training"
shorttitle        : "Decision models and experience-dependent plasticity"
author: 
  - name          : "Samantha Parker"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "School of Psychological Sciences, 16 University Avenue, Macquarie University, NSW 2109"
    email         : "samantha.parker@students.mq.edu.au"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal analysis"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Emily S. Cross"
    affiliation   : "2"
    role:
      - "Conceptualization"
      - "Resources"
      - "Writing - Review & Editing"
  - name          : "Richard Ramsey"
    affiliation   : "2"
    role:
      - "Conceptualization"
      - "Visualisation"
      - "Supervision"
      - "Project Administration"
      - "Validation"
      - "Writing - Review & Editing"
affiliation:
  - id            : "1"
    institution   : "Macquarie University"
  - id            : "2"
    institution   : "ETH Zürich"
authornote: |
  Samantha Parker. School of Psychological Sciences, Macquarie University.
  Emily S. Cross. Social Brain Sciences Lab, Department of Humanities, Social and Political Sciences (D-GESS), ETH Zürich.
  Richard Ramsey. Neural Control of Movement Lab, Department of Health Sciences and Technology (D-HEST) and Social Brain Sciences Lab, Department of Humanities, Social and Political Sciences (D-GESS), ETH Zürich.
  <!-- Enter author note here. -->
abstract: |
  Evidence accumulation modelling has been shown to uncover new insights into the cognitive mechanisms that underlie decision making from behavioural data. By jointly modelling reaction time and accuracy data, such decision models estimate latent variables that represent distinct computaitonal processes, such as stimulus encoding, response caution and the quality of information processing. In this study we use an evidence accumulation model, the Linear Ballistic Accumulator (LBA), to shed new light into the mechanisms that underlie learning based on linguistic and action-based training. The LBA model is applied to behavioural data from a previously published training study where participants learn to name, tie or name and tie a set of knots. Our results show that training is multifaceted and associated with an increase in stimulus-encoding time, a reduction in response caution, as well as an increase in the speed of information accumulation. Furthermore, the results showed that there was an added benefit to the rate of evidence accumulation when naming and tying experience were combined. This latter finding suggests that performance benefits from multi-modal training may be instantiated in computational processes that are associated with the quantity and quality of information accumulation during decision making. Overall, in applying this computational approach to accuracy and reaction time data, we uncover new insights into the mechanisms that govern experience-dependent plasticity.

  *Public significance statement:* The results of this study show that multi-modal training, which spans linguistic and action-based content, increases the quality of information that is gained through perception to make a decision. These results provide a novel computational account of performance benefits that are often observed from multi-modal training, which will aid theory development on learning and plasticity within cognitive science.

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity"
wordcount         : "6698"
bibliography      : ["references.bib", "r-references.bib"]
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man, donotrepeattitle"
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
note              : "\\clearpage" ## this moves the author note section to a second page
editor_options: 
  chunk_output_type: console
header-includes:
  - \raggedbottom
---

@@

We applied the LBA model to a previously published dataset from Cross and colleagues (2012). This study used fMRI to examine brain activity whilst participants completed a speeded perceptual discrimination task before and after training. The data used in the current study, therefore, were collected in 2006. Training consisted of participants learning to name 10 knots, tie 10 knots and name and tie a further 10 knots, while a final 10 knots remained untrained (i.e., no information about how to tie the knot or what it was called was experienced during the training period). Before and after the knot training portion of the study, participants were required to complete 80 trials of a perceptual discrimination task. In this task, participants had to decide whether two photographs were of the same or different knots. Each pair of knots was selected from the same learning class (i.e., name, tie, both name and tie or untrained knots). When photographs were of the same knot, the viewing angle of the two photographs differed, so the stimuli presented were never identical. Of the 80 trials, 50% of the knots were the same and 50% of the knots were different. Both accuracy and response times (ms) of the perceptual discrimination task were recorded. As we were interested in modelling only the behavioural results of the perceptual discrimination task, we summarise the aspects of the dataset relevant to the present study below and refer readers to the original paper for all other details (see Cross et al., 2012).

@@

There was some evidence of an effect of training type on accuracy (see Figure 1A). Relative to the untrained condition (M = 87.4, SD = 33.3) accuracy was higher for knots that received both naming and tying training (M = 88.9, SD = 31.5), but was lower in both the tying (M = 85.1, SD = 35.6) and naming conditions (M = 83.8, SD = 36.9). There also appeared to be an effect of training type in RT (see Figure 1B) relative to knots that received no training (M = 1139 ms, SD = 345 ms), participants responded faster to knots that received naming training (M = 1055 ms, SD = 347 ms), tying training (M = 1119 ms, SD = 356 ms) and knots that received both naming and tying training tying training (M = 1082 ms, SD = 344 ms).

@@

Inspection of the posterior distributions for the threshold parameter of the LBA model revealed evidence to suggest that thresholds significantly differed by Training Type. Specifically, thresholds were lower in all three training conditions, naming (0.76 [0.64, 0.88]), tying, (0.68 [0.57, 0.79]) and both naming and tying training (1.01 [0.84, 1.19]) relative to the untrained condition (2.80 [2.60, 3.03]) (see Figure 2A).

@@

The aim of the present study was to use evidence accumulation modelling to investigate the cognitive mechanisms that underlie linguistic and action-based training in a simple knot-tying and knot-naming task. Our results revealed that the effects of training are multifaceted, in terms of the latent cognitive processes involved. In other words, training impacted several cognitive sub-processes that, in combination, determine subsequent task performance. In addition, an added benefit was observed for the speed of information accumulation when naming and tying experience were combined. This latter finding suggests that a multi-modal training protocol can aid the quantity and quality of information processing during decision making. Below, we discuss several ways in which our findings advance our understanding of how cognitive systems are shaped by different types of knowledge acquisition and experience. More generally, we also outline why future work may benefit from taking a more computational approach to understand the effects of training on learning and performance.

@@

A second interpretation is that the unique combination of linguistic and action-based training may somehow enhance the quality and quantity of information accumulation during decision making. Such a qualitative interpretation would be consistent with prior studies that have reported multi-modal training protocols to lead to greater improvements in cognitive functions such as visuospatial working and episodic memory, executive functioning and the speed of information processing than single-function training protocols, as well as studies that report multi-model training protocols to engage a broad network of sensorimotor brain regions more than unimodal training protocols [@kirschAdditiveRoutesAction2015]. In the present study, we were unable to tease apart whether the results reflect a dose-response effect or instead reflect a qualitatively different impact of multi-modal training. We encourage future studies to systematically manipulate the combination of training types to determine whether increased exposure to training and/or different types of training influence the quality and rate at which evidence accumulates about a decision.

>>>>

---
title             : "Evidence accumulation modelling offers new insights into the cognitive mechanisms that underlie linguistic and action-based training"
shorttitle        : "Decision models and experience-dependent plasticity"
author: 
  - name          : "Samantha Parker"
    affiliation   : "1"
    # corresponding : yes    # Define only one corresponding author
    # address       : "School of Psychological Sciences, 16 University Avenue, Macquarie University, NSW 2109"
    # email         : "samantha.parker@students.mq.edu.au"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal analysis"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Emily S. Cross"
    affiliation   : "2"
    role:
      - "Conceptualization"
      - "Resources"
      - "Writing - Review & Editing"
  - name          : "Richard Ramsey"
    affiliation   : "2"
    corresponding : yes    # Define only one corresponding author
    email         : "richard.ramsey@hest.ethz.ch"
    role:
      - "Conceptualization"
      - "Visualisation"
      - "Supervision"
      - "Project Administration"
      - "Validation"
      - "Writing - Review & Editing"
affiliation:
  - id            : "1"
    institution   : "Macquarie University"
  - id            : "2"
    institution   : "ETH Zürich"
authornote: |
  Samantha Parker. School of Psychological Sciences, Macquarie University.
  Emily S. Cross. Social Brain Sciences Lab, Department of Humanities, Social and Political Sciences (D-GESS), ETH Zürich.
  Richard Ramsey. Neural Control of Movement Lab, Department of Health Sciences and Technology (D-HEST) and Social Brain Sciences Lab, Department of Humanities, Social and Political Sciences (D-GESS), ETH Zürich.
  <!-- Enter author note here. -->
abstract: |
  Evidence accumulation modelling has been shown to uncover new insights into the cognitive mechanisms that underlie decision making from behavioural data. By jointly modelling reaction time and accuracy data, such decision models estimate latent variables that represent distinct computaitonal processes, such as stimulus encoding, response caution and the quality of information processing. In this study we use an evidence accumulation model, the Linear Ballistic Accumulator (LBA), to shed new light into the mechanisms that underlie learning based on linguistic and action-based training. The LBA model is applied to behavioural data from a previously published training study where participants learn to name, tie or name and tie a set of knots. Our results show that training is multifaceted and associated with an increase in stimulus-encoding time, a reduction in response caution, as well as an increase in the speed of information accumulation. Furthermore, the results showed that there was an added benefit to the rate of evidence accumulation when naming and tying experience were combined. This latter finding suggests that performance benefits from multi-modal training may be instantiated in computational processes that are associated with the quantity and quality of information accumulation during decision making. Overall, in applying this computational approach to accuracy and reaction time data, we uncover new insights into the mechanisms that govern experience-dependent plasticity.

  <!-- *Public significance statement:* The results of this study show that multi-modal training, which spans linguistic and action-based content, increases the quality of information that is gained through perception to make a decision. These results provide a novel computational account of performance benefits that are often observed from multi-modal training, which will aid theory development on learning and plasticity within cognitive science.  -->

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity"
wordcount         : "6967"
bibliography      : ["references.bib", "r-references.bib"]
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man, donotrepeattitle"
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
note              : "\\clearpage" ## this moves the author note section to a second page
editor_options: 
  chunk_output_type: console
header-includes:
  - \raggedbottom
---

@@

We applied the LBA model to a previously published dataset from (Cross et al., 2012). Cross and colleagues (2012) used fMRI to examine brain activity whilst participants completed a speeded perceptual discrimination task before and after training. The data used in the current study, therefore, were collected in 2006. Training consisted of participants learning to name 10 knots, tie 10 knots and name and tie a further 10 knots, while a final 10 knots remained untrained (i.e., no information about how to tie the knot or what it was called was experienced during the training period). Before and after the knot training portion of the study, participants were required to complete 80 trials of a perceptual discrimination task. In this task, participants had to decide whether two photographs were of the same or different knots. Each pair of knots was selected from the same learning class (i.e., name, tie, both name and tie or untrained knots). When photographs were of the same knot, the viewing angle of the two photographs differed, so the stimuli presented were never identical. Of the 80 trials, 50% of the knots were the same and 50% of the knots were different. Both accuracy and response times (ms) of the perceptual discrimination task were recorded. As we were interested in modelling only the behavioural results of the perceptual discrimination task, we summarise the aspects of the dataset relevant to the present study below and refer readers to the original paper for all other details (see Cross et al., 2012).

@@

There was some evidence of an effect of training type on accuracy (see Figure 1A). Relative to the untrained condition (M = 87.4, SEM = 7.84) accuracy was higher for knots that received both naming and tying training (M = 88.9, SEM = 7.42), but was lower in both the tying (M = 85.1, SEM = 8.40) and naming conditions (M = 83.8, SEM = 8.71). There also appeared to be an effect of training type in RT (see Figure 1B) relative to knots that received no training (M = 1139 ms, SEM = 81.2 ms), participants responded faster to knots that received naming training (M = 1055 ms, SEM = 81.9 ms), tying training (M = 1119 ms, SEM = 83.9 ms) and knots that received both naming and tying training tying training (M = 1082 ms, SEM = 81.1 ms).

@@

Inspection of the posterior distributions for the threshold parameter of the LBA model revealed evidence to suggest that thresholds differed by Training Type. Specifically, thresholds were lower in all three training conditions, naming (0.76 [0.64, 0.88]), tying, (0.68 [0.57, 0.79]) and both naming and tying training (1.01 [0.84, 1.19]) relative to the untrained condition (2.80 [2.60, 3.03]) (see Figure 2A).

@@

The aim of the present study was to use evidence accumulation modelling to investigate the cognitive mechanisms that underlie linguistic and action-based training in a knot-tying and knot-naming task. Our results revealed that the effects of training are multifaceted, in terms of the latent cognitive processes involved. In other words, training impacted several cognitive sub-processes that, in combination, determine subsequent task performance. In addition, an added benefit was observed for the speed of information accumulation when naming and tying experience were combined. This latter finding suggests that a multi-modal training protocol can aid the quantity and quality of information processing during decision making. Below, we discuss several ways in which our findings advance our understanding of how cognitive systems are shaped by different types of knowledge acquisition and experience. More generally, we also outline why future work may benefit from taking a more computational approach to understand the effects of training on learning and performance.

@@

A second interpretation is that the unique combination of linguistic and action-based training may lead to a qualitative difference in information accumulation during decision making. Such a qualitative interpretation would be consistent with prior studies that have shown that compared to uni-modal training protocols, multi-modal training leads to greater improvements in cognitive domains such as working memory and propblem solving [@ward2017], as well as greater engagement of a broad network of sensorimotor brain regions [@kirschAdditiveRoutesAction2015]. In the present study, we were unable to tease apart whether the results reflect a dose-response effect or instead reflect a qualitatively different impact of multi-modal training. We encourage future studies to systematically manipulate the combination of training types to determine whether increased exposure to training and/or different types of training influence the quality and rate at which evidence accumulates about a decision.

### 2025-04-01 manuscript/manuscript.tex
minor updates to the manuscript

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\makeatother
\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6698}
\usepackage{lineno}

@@

Correspondence concerning this article should be addressed to Samantha Parker, School of Psychological Sciences, 16 University Avenue, Macquarie University, NSW 2109. E-mail: \href{mailto:samantha.parker@students.mq.edu.au}{\nolinkurl{samantha.parker@students.mq.edu.au}}

@@

\abstract{%
Evidence accumulation modelling has been shown to uncover new insights into the cognitive mechanisms that underlie decision making from behavioural data. By jointly modelling reaction time and accuracy data, such decision models estimate latent variables that represent distinct computaitonal processes, such as stimulus encoding, response caution and the quality of information processing. In this study we use an evidence accumulation model, the Linear Ballistic Accumulator (LBA), to shed new light into the mechanisms that underlie learning based on linguistic and action-based training. The LBA model is applied to behavioural data from a previously published training study where participants learn to name, tie or name and tie a set of knots. Our results show that training is multifaceted and associated with an increase in stimulus-encoding time, a reduction in response caution, as well as an increase in the speed of information accumulation. Furthermore, the results showed that there was an added benefit to the rate of evidence accumulation when naming and tying experience were combined. This latter finding suggests that performance benefits from multi-modal training may be instantiated in computational processes that are associated with the quantity and quality of information accumulation during decision making. Overall, in applying this computational approach to accuracy and reaction time data, we uncover new insights into the mechanisms that govern experience-dependent plasticity.

\emph{Public significance statement:} The results of this study show that multi-modal training, which spans linguistic and action-based content, increases the quality of information that is gained through perception to make a decision. These results provide a novel computational account of performance benefits that are often observed from multi-modal training, which will aid theory development on learning and plasticity within cognitive science.
}

@@

We applied the LBA model to a previously published dataset from Cross and colleagues (2012). This study used fMRI to examine brain activity whilst participants completed a speeded perceptual discrimination task before and after training. The data used in the current study, therefore, were collected in 2006. Training consisted of participants learning to name 10 knots, tie 10 knots and name and tie a further 10 knots, while a final 10 knots remained untrained (i.e., no information about how to tie the knot or what it was called was experienced during the training period). Before and after the knot training portion of the study, participants were required to complete 80 trials of a perceptual discrimination task. In this task, participants had to decide whether two photographs were of the same or different knots. Each pair of knots was selected from the same learning class (i.e., name, tie, both name and tie or untrained knots). When photographs were of the same knot, the viewing angle of the two photographs differed, so the stimuli presented were never identical. Of the 80 trials, 50\% of the knots were the same and 50\% of the knots were different. Both accuracy and response times (ms) of the perceptual discrimination task were recorded. As we were interested in modelling only the behavioural results of the perceptual discrimination task, we summarise the aspects of the dataset relevant to the present study below and refer readers to the original paper for all other details (see Cross et al., 2012).

@@

Inspection of the posterior distributions for the threshold parameter of the LBA model revealed evidence to suggest that thresholds significantly differed by Training Type. Specifically, thresholds were lower in all three training conditions, naming (0.76 {[}0.64, 0.88{]}), tying, (0.68 {[}0.57, 0.79{]}) and both naming and tying training (1.01 {[}0.84, 1.19{]}) relative to the untrained condition (2.80 {[}2.60, 3.03{]}) (see Figure 2A).

@@

A second interpretation is that the unique combination of linguistic and action-based training may somehow enhance the quality and quantity of information accumulation during decision making. Such a qualitative interpretation would be consistent with prior studies that have reported multi-modal training protocols to lead to greater improvements in cognitive functions such as visuospatial working and episodic memory, executive functioning and the speed of information processing than single-function training protocols, as well as studies that report multi-model training protocols to engage a broad network of sensorimotor brain regions more than unimodal training protocols (Kirsch \& Cross, 2015). In the present study, we were unable to tease apart whether the results reflect a dose-response effect or instead reflect a qualitatively different impact of multi-modal training. We encourage future studies to systematically manipulate the combination of training types to determine whether increased exposure to training and/or different types of training influence the quality and rate at which evidence accumulates about a decision.

@@

Second, consistent with prior studies, our results revealed training effects to be multifaceted. That is, training effects were evident across a number of parameters of the LBA model, rather than a single parameter (Dutilh et al., 2011; Dutilh et al., 2009; Reinhartz et al., 2023). This suggests that improvements in task performance that are associated with training can be attributed to a number of underlying mechanisms. It may also be one reason for the wide variety of training-induced outcomes that are observed across different tasks and training protocols, as it is possible that different types and amounts of training can impact underlying cognitive processes in different ways. And this is one clear benefit to understanding cognitive processes that is provided by taking a more mathematical approach to theory building in psychology and cognitive neuroscience, as it forces a more explicit formulation of the relationship between parts of a system that are under investigation (Hintzman, 1991; Yarkoni, 2022/ed).

@@

@@

\bibitem[\citeproctext]{ref-yarkoni2022}
Yarkoni, T. (2022/ed). The generalizability crisis. \emph{Behavioral and Brain Sciences}, \emph{45}, e1. \url{https://doi.org/10.1017/S0140525X20001685}

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\makeatother
\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6967}
\usepackage{lineno}

@@

Correspondence concerning this article should be addressed to Richard Ramsey. E-mail: \href{mailto:richard.ramsey@hest.ethz.ch}{\nolinkurl{richard.ramsey@hest.ethz.ch}}

@@

\abstract{%
Evidence accumulation modelling has been shown to uncover new insights into the cognitive mechanisms that underlie decision making from behavioural data. By jointly modelling reaction time and accuracy data, such decision models estimate latent variables that represent distinct computaitonal processes, such as stimulus encoding, response caution and the quality of information processing. In this study we use an evidence accumulation model, the Linear Ballistic Accumulator (LBA), to shed new light into the mechanisms that underlie learning based on linguistic and action-based training. The LBA model is applied to behavioural data from a previously published training study where participants learn to name, tie or name and tie a set of knots. Our results show that training is multifaceted and associated with an increase in stimulus-encoding time, a reduction in response caution, as well as an increase in the speed of information accumulation. Furthermore, the results showed that there was an added benefit to the rate of evidence accumulation when naming and tying experience were combined. This latter finding suggests that performance benefits from multi-modal training may be instantiated in computational processes that are associated with the quantity and quality of information accumulation during decision making. Overall, in applying this computational approach to accuracy and reaction time data, we uncover new insights into the mechanisms that govern experience-dependent plasticity.
}

@@

We applied the LBA model to a previously published dataset from (Cross et al., 2012). Cross and colleagues (2012) used fMRI to examine brain activity whilst participants completed a speeded perceptual discrimination task before and after training. The data used in the current study, therefore, were collected in 2006. Training consisted of participants learning to name 10 knots, tie 10 knots and name and tie a further 10 knots, while a final 10 knots remained untrained (i.e., no information about how to tie the knot or what it was called was experienced during the training period). Before and after the knot training portion of the study, participants were required to complete 80 trials of a perceptual discrimination task. In this task, participants had to decide whether two photographs were of the same or different knots. Each pair of knots was selected from the same learning class (i.e., name, tie, both name and tie or untrained knots). When photographs were of the same knot, the viewing angle of the two photographs differed, so the stimuli presented were never identical. Of the 80 trials, 50\% of the knots were the same and 50\% of the knots were different. Both accuracy and response times (ms) of the perceptual discrimination task were recorded. As we were interested in modelling only the behavioural results of the perceptual discrimination task, we summarise the aspects of the dataset relevant to the present study below and refer readers to the original paper for all other details (see Cross et al., 2012).

@@

Inspection of the posterior distributions for the threshold parameter of the LBA model revealed evidence to suggest that thresholds differed by Training Type. Specifically, thresholds were lower in all three training conditions, naming (0.76 {[}0.64, 0.88{]}), tying, (0.68 {[}0.57, 0.79{]}) and both naming and tying training (1.01 {[}0.84, 1.19{]}) relative to the untrained condition (2.80 {[}2.60, 3.03{]}) (see Figure 2A).

@@

A second interpretation is that the unique combination of linguistic and action-based training may lead to a qualitative difference in information accumulation during decision making. Such a qualitative interpretation would be consistent with prior studies that have shown that compared to uni-modal training protocols, multi-modal training leads to greater improvements in cognitive domains such as working memory and propblem solving (Ward et al., 2017), as well as greater engagement of a broad network of sensorimotor brain regions (Kirsch \& Cross, 2015). In the present study, we were unable to tease apart whether the results reflect a dose-response effect or instead reflect a qualitatively different impact of multi-modal training. We encourage future studies to systematically manipulate the combination of training types to determine whether increased exposure to training and/or different types of training influence the quality and rate at which evidence accumulates about a decision.

@@

Second, consistent with prior studies, our results revealed training effects to be multifaceted. That is, training effects were evident across a number of parameters of the LBA model, rather than a single parameter (Dutilh et al., 2011; Dutilh et al., 2009; Reinhartz et al., 2023). This suggests that improvements in task performance that are associated with training can be attributed to a number of underlying mechanisms. It may also be one reason for the wide variety of training-induced outcomes that are observed across different tasks and training protocols, as it is possible that different types and amounts of training can impact underlying cognitive processes in different ways. And this is one clear benefit to understanding cognitive processes that is provided by taking a more mathematical approach to theory building in psychology and cognitive neuroscience, as it forces a more explicit formulation of the relationship between parts of a system that are under investigation (Hintzman, 1991; Yarkoni, 2022).

@@

\bibitem[\citeproctext]{ref-ward2017}
Ward, N., Paul, E., Watson, P., Cooke, G. E., Hillman, C. H., Cohen, N. J., \ldots{} Barbey, A. K. (2017). Enhanced {Learning} through {Multimodal Training}: {Evidence} from a {Comprehensive Cognitive}, {Physical Fitness}, and {Neuroscience Intervention}. \emph{Scientific Reports}, \emph{7}(1), 5808. \url{https://doi.org/10.1038/s41598-017-06237-5}

@@

\bibitem[\citeproctext]{ref-yarkoni2022}
Yarkoni, T. (2022). The generalizability crisis. \emph{Behavioral and Brain Sciences}, \emph{45}, e1. \url{https://doi.org/10.1017/S0140525X20001685}
